---
title: "hw1"
author: "haoming lei"
date: "1/14/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Obtain a histogram for each of the variables
library("readxl")
mydata=cars931 <- read_excel("C:/Users/Administrator/Desktop/sta137/cars931.xlsx")
head(mydata)
Y=log(mydata$Price)
X1=log(mydata$`City mpg`)
X2=log(mydata$`Hwy mpg`)
X3=log(mydata$`Engine size`)
X4=sqrt(mydata$HP)
X5=mydata$Tank
X6=mydata$Weight
hist(Y,main="Distribution of Price")#Bimodal distribution
hist(X1,main="Distribution of City mpg")#right-skewed distribution 
hist(X2,main="Distribution of Hwy mpg")#Bimodal distribution
hist(X3,main="Distribution of Engine size")#Plateau distribution  
hist(X4,main="Distribution of HP")#Edqe peak distribution
hist(X5,main="Distribution of Tank")#Bimodal distribution
hist(X6,main="Distribution of Weight")#Plateau distribution 
#结论
```

Appendix

library("readxl")

mydata=cars931 <- read_excel("C:/Users/Administrator/Desktop/sta137/cars931.xlsx")

head(mydata)

Y=log(mydata$Price)

X1=log(mydata$`City mpg`)
X2=log(mydata$`Hwy mpg`)

X3=log(mydata$`Engine size`)

X4=sqrt(mydata$HP)

X5=mydata$Tank

X6=mydata$Weight

hist(Y,main="Distribution of Price")#Bimodal distribution

hist(X1,main="Distribution of City mpg")#right-skewed distribution 

hist(X2,main="Distribution of Hwy mpg")#Bimodal distribution

hist(X3,main="Distribution of Engine size")#Plateau distribution  

hist(X4,main="Distribution of HP")#Edqe peak distribution

hist(X5,main="Distribution of Tank")#Bimodal distribution

hist(X6,main="Distribution of Weight")#Plateau distribution 